\chapter{Searching maps}

Client code does not manipulate maps directly.  Instead, it uses some
\emph{state} object supplied by \sysname{}.

\Defprotoclass {state}

This class is the protocol class for all states.

\Defgeneric {path} {state}

This generic function returns a \emph{path}, i.e. a list of keys that
have been supplied so far, and that resulted in \texttt{state}.

\Defclass {internal-state}

This class is a subclass of the class \texttt{state}.  It represents a
\emph{partial result} in that the sequence of keys supplied to the
search so far corresponds to a map, and not to a leaf object.

\Defgeneric {map} {internal-state}

Given an internal state, this generic function returns the map
associated with that state.

\Defclass {final-state}

This class is a subclass of the class \texttt{state}.  It represents a
\emph{final result} in that the sequence of keys supplied so far
corresponds to a leaf object.

\Defgeneric {object} {final-state}

Given a final state, this generic function returns the leaf object
associated with that state.

\Defclass {error-state}

This class is a subclass of the class \texttt{state}.  It represents a
situation where the sequence of keys supplied so far contains at least
one key that is associated with neither another map nor with a leaf
object in the corresponding map.

\Defun {make-initial-state} {map}

This function creates an instance of the class
\texttt{internal-state}.  The map associated with that internal state
(as returned by the generic function \texttt{map}) is the argument
\texttt{map}, and the path associated with that internal state (as
returned by the generic function \texttt{path}) is the empty list.

\Defgeneric {advance} {internal-state key}

This generic function is used to advance from one state to another.
The argument \texttt{key} is used in the map associated with
\texttt{internal-state} (as returned by the generic function
\texttt{map}) to look up the entity being mapped to.  If that entity
is another map, then this function returns an instance of the class
\texttt{internal-state}.  If that entity is a leaf object, then this
function returns an instance of the class \texttt{final-state}.  If
there is no entity associated with \emph{key} in the map associated
with \texttt{internal-state}, then an instance of the class
\texttt{error-state} is returned.

In all cases, the path of the resulting state (as returned by the
generic function \texttt{path}) is the path resulting from adding
\texttt{key} to the end of the path associated with
\texttt{internal-state}.

\Defgeneric {possible-completions} {state}

This generic function returns a set of keys (represented as a list),
each of which can be used as the second argument to the generic
function \texttt{advance} when the first argument is \texttt{state}.
If \texttt{state} is not an instance of the class named
\texttt{internal-state}, or if there are no keys in the map associated
with \texttt{state}, then the empty list is returned.
